### 2014-01-14 src/paper.Rnw
update

<<a,message=F, echo=F>>=
require(xtable)
require(data.table)
@

@@

Analysis

@@

Results

>>>>

<<a,message=F, echo=F>>=
require(xtable)
require(data.table)
load('data/mu.rda')
@

@@

<<prepare,echo=F>>=
attach(m)
sdl_f <- mut.avg~mut.avg.sdl + 0
rnd_f <- mut.avg~mut.avg.rnd + 0

sdl_all <- lm(sdl_f)
rnd_all <- lm(rnd_f)

sdl_s <- summary(sdl_all)
rnd_s <- summary(rnd_all)

avg.est <- sdl_s$coefficients['mut.avg.sdl','Estimate']
rnd.est <- rnd_s$coefficients['mut.avg.rnd','Estimate']
@

\begin{figure*}[t]
<<plots, fig.width=5, fig.height=5, out.width='.45\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
plot(sdl_f, main='SDL ~ ALL',pch='*')
abline(sdl_all, col='red')
plot(rnd_f, main='RND ~ ALL',pch='*')
abline(rnd_all, col='blue')
abline(sdl_all, col='red', lty=2)
@
\caption{Plots}
\label{fig:caddrm}
\end{figure*}

\subsection{Correlation Analysis}

$ \mu_{all} = 0 + \beta_0 \times \mu_{sample}  $

The interesting part is (1) the $\beta_0$ coeff which tells how much we must multiply the  sampled/selected score to get original score, and $R^2$ which tells us how close the score   is.

\subsubsection{mut.avg.sdl and mut.avg}

$ \mu_{all} = 0 + \Sexpr{avg.est} \times \mu_{sdl}  $

\subsubsection{mut.avg.rnd and mut.avg}

$ \mu_{all} = 0 + \Sexpr{rnd.est} \times \mu_{rnd}  $

@@

We see from the data that random sampling has a higher $R^2$, and also approximates the all  mutations score better.
However, caveat emptor. There is a difference between the number of mutators for SDL and RAND. If our approximation was right, we should have gotten nearly same number of mutators. However
The number of mutators in RND is \Sexpr{sum(m$pit.mutation.total.rnd) / sum(m$pit.mutation.total.sdl)} times SDL.
